---
title: "Final Project"
author: " Yu Liu (Ning Ning)"
date: "June 3th 2018"
output:
  ioslides_presentation
---
## Location
Location: Bangkok, Thailand

```{r, echo=FALSE, message=FALSE}
library(plotly)
plot_ly(
  type = 'scattergeo',
  lon=c(100.5018),
  lat=c(13.7563),
  text=('Thailand'),
  mode='markers')
```


## Single Detached Housing

Summary Table for Index

 Min.    1stQu  Median   Mean    3rdQu.  Max.    Var    Std
------  ------  ------  ------  ------  ------  ------  ------  
100.4   108.3   121.7    119.6   129.2  138.1   123.6    11.1


Summary Table for Growth (%Y-O-Y)

 Min.     1stQu  Median   Mean  3rdQu.    Max.    Var    Std
------  ------  ------  ------  ------  ------  ------  ------  
-3.200   1.100   3.600    3.568   5.800  10.600  9.46    11.1


## Town House

Summary Table for Index

 Min.     1stQu  Median   Mean  3rdQu.    Max.    Var    Std
------  ------  ------  ------  ------  ------  ------  ------  
97.7     105.8   124.9   121.9   129.2   135.9  239.5    15.5



Summary Table for Growth (%Y-O-Y)

 Min.     1stQu  Median   Mean  3rdQu.    Max.    Var    Std
------  ------  ------  ------  ------  ------  ------  ------  
-1.400   2.300   3.800   4.659   7.200  14.000   13.4    3.7

## Condo

Summary Table for Index

 Min.     1stQu  Median   Mean  3rdQu.    Max.    Var    Std
------  ------  ------  ------  ------  ------  ------  ------  
112.4    126.0   139.8   141.8   160.8   181.6  427.04   20.67


Summary Table for Growth (%Y-O-Y)

 Min.     1stQu  Median   Mean  3rdQu.    Max.    Var    Std
------  ------  ------  ------  ------  ------  ------  ------  
-3.600   2.900   6.100   5.903   8.400  14.400   15.42   3.93

## land

Summary Table for Index

 Min.     1stQu  Median   Mean  3rdQu.    Max.    Var    Std
------  ------  ------  ------  ------  ------  ------  ------  
102.8    116.7   137.7   139.3   167.1   178.3  594.04   24.37


Summary Table for Growth (%Y-O-Y)

 Min.     1stQu  Median   Mean  3rdQu.    Max.    Var    Std
------  ------  ------  ------  ------  ------  ------  ------  
-5.500   1.900   6.293   9.900   16.90   14.40   24.98   4.998

## Graph for Minimum (Index)
1 - Single Detached Housing
2 - Town House
3 - Condo
4 - Land
```{r, echo=FALSE, message=FALSE}
library(plotly)

plot_ly(x = c(1,2,3,4),
        y=c(100.4,97.7,112.4,102.8),
        type='scatter',
        mode='markers')

```


## Graph for Min. (%Y-O-Y)
1 - Single Detached Housing
2 - Town House
3 - Condo
4 - Land
```{r, echo=FALSE, message=FALSE}
library(plotly)

plot_ly(x = c(1,2,3,4),
        y=c(-5.5,-3.6,-1.4,-3.2),
        type='scatter',
        mode='markers')

```

## Graph for 1stQu (Index)
1 - Single Detached Housing
2 - Town House
3 - Condo
4 - Land
```{r, echo=FALSE, message=FALSE}
library(plotly)

plot_ly(x = c(1,2,3,4),
        y=c(108.3,105.8,126,116.7),
        type='scatter',
        mode='markers')

```


## Graph for 1stQu (%Y-O-Y)
1 - Single Detached Housing
2 - Town House
3 - Condo
4 - Land
```{r, echo=FALSE, message=FALSE}
library(plotly)

plot_ly(x = c(1,2,3,4),
        y=c(1.1,2.3,2.9,1.9),
        type='scatter',
        mode='markers')

```


## Graph for Median (Index)
1 - Single Detached Housing
2 - Town House
3 - Condo
4 - Land
```{r, echo=FALSE, message=FALSE}
library(plotly)

plot_ly(x = c(1,2,3,4),
        y=c(119.6,121.9,141.8,139.3),
        type='scatter',
        mode='markers')

```
      
## Graph for Median (%Y-O-Y)
1 - Single Detached Housing
2 - Town House
3 - Condo
4 - Land
```{r, echo=FALSE, message=FALSE}
library(plotly)

plot_ly(x = c(1,2,3,4),
        y=c(3.6,3.8,6.1,6.293),
        type='scatter',
        mode='markers')

```

## Graph for Mean (Index)
1 - Single Detached Housing
2 - Town House
3 - Condo
4 - Land
```{r, echo=FALSE, message=FALSE}
library(plotly)

plot_ly(x = c(1,2,3,4),
        y=c(121.7,121.9,141.8,139.3),
        type='scatter',
        mode='markers')

```

## Graph for Mean (%Y-O-Y)
1 - Single Detached Housing
2 - Town House
3 - Condo
4 - Land
```{r, echo=FALSE, message=FALSE}
library(plotly)

plot_ly(x = c(1,2,3,4),
        y=c(3.568,4.659,5.903,9.9),
        type='scatter',
        mode='markers')

```

## Graph for 3rdQu (Index)
1 - Single Detached Housing
2 - Town House
3 - Condo
4 - Land
```{r, echo=FALSE, message=FALSE}
library(plotly)

plot_ly(x = c(1,2,3,4),
        y=c(119.6,129.2,160.8,167.1),
        type='scatter',
        mode='markers')

```
  
## Graph for 3rdQu. (%Y-O-Y)
1 - Single Detached Housing
2 - Town House
3 - Condo
4 - Land
```{r, echo=FALSE, message=FALSE}
library(plotly)

plot_ly(x = c(1,2,3,4),
        y=c(5.8,7.2,8.4,16.9),
        type='scatter',
        mode='markers')

```

## Graph for Max. (Index)
1 - Single Detached Housing
2 - Town House
3 - Condo
4 - Land
```{r, echo=FALSE, message=FALSE}
library(plotly)

plot_ly(x = c(1,2,3,4),
        y=c(138.1,135.9,181.6,178.3),
        type='scatter',
        mode='markers')

```

## Graph for Max. (%Y-O-Y)
1 - Single Detached Housing
2 - Town House
3 - Condo
4 - Land
```{r, echo=FALSE, message=FALSE}
library(plotly)

plot_ly(x = c(1,2,3,4),
        y=c(10.600,14,14.400,14.40),
        type='scatter',
        mode='markers')

```

## Graph for Var (Index)
1 - Single Detached Housing
2 - Town House
3 - Condo
4 - Land
```{r, echo=FALSE, message=FALSE}
library(plotly)

plot_ly(x = c(1,2,3,4),
        y=c(123.6,239.5,427.04,594.04),
        type='scatter',
        mode='markers')

```

## Graph for Var (%Y-O-Y)
1 - Single Detached Housing
2 - Town House
3 - Condo
4 - Land
```{r, echo=FALSE, message=FALSE}
library(plotly)

plot_ly(x = c(1,2,3,4),
        y=c(9.46,13.4,15.24,24.98),
        type='scatter',
        mode='markers')

```

## Graph for Std (Index)
1 - Single Detached Housing
2 - Town House
3 - Condo
4 - Land
```{r, echo=FALSE, message=FALSE}
library(plotly)

plot_ly(x = c(1,2,3,4),
        y=c(11.1,15.5,20.67,24.37),
        type='scatter',
        mode='markers')

```

## Graph for Std (%Y-O-Y)
1 - Single Detached Housing
2 - Town House
3 - Condo
4 - Land
```{r, echo=FALSE, message=FALSE}
library(plotly)

plot_ly(x = c(1,2,3,4),
        y=c(11.1,3.7,3.93,4.998),
        type='scatter',
        mode='markers')

```

